Smoking and COVID Living Review (v10): a bayesian analysis

### 2021-01-28 reports/bayesian_report.Rmd
from mac

  html_document:
    code_folding: hide
    highlight: zenburn
    number_sections: true
    theme: spacelab
    toc: false
    toc_collapse: true
    toc_depth: 3
    toc_float: yes
    css: !expr here::here('css', 'style.css')
    keep_md: false
editor_options: 
  chunk_output_type: inline
---
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      warning = F,
                      message = F)
options(width = 180)
unlink('reports/markdown_report_cache', recursive = TRUE)

```
# Data preparation {.tabset .tabset-fade .tabset-pills}

## Load packages
* **Load packages**: load packages and useful scripts for the analysis
* **Load scripts**: We have written functions to handle much of the Bayesian analysis
* **Load Bayesian datasets**: The Bayesian approach relies on large simulated datasets from the observed data, for this report we will only present the results graphically from data we have simulated elsewhere. The scripts `bayes_scripts.R`, `bayesian_data_generation.R` and `bayesian_analysis.R` should be able to be run locally if you want to generate your own simulated data. Alternatively you can use the pre-generated data which is stored in the `data_clean\bayesian_models` folder in the github repository [here](https://github.com/DidDrog11/smoking_covid/tree/master) and then you can skip the `bayesian_data_generation.R` step.
```{r load_packages, include=FALSE, quietly=T}
source(here::here("scripts", "libraries.R"))
```

```{r load_dictionary}
source(here("scripts", "author_dictionary.R"))
```
## Download data
``` {r google_data}
google_api <- rstudioapi::askForSecret("Google API Key")
register_google(google_api)
drive_download("https://docs.google.com/spreadsheets/d/1jelIGxrm99QpDKwSoyMUliDJQWtzk4bHsNGDaIjxTaU/edit?usp=sharing", path = here("data_spreadsheet", "data_extraction_current.xlsx"), overwrite = T)

@@

The pull requests from the API may happen too rapidly if this is run as a chunk so it's better to run this line by line.

@@

```{r head_search_details}
flextable(search_details[,1:13])
```
The second sheet is **General study details** this includes the lead author, where the study is published, the date it was published, the country in which the data originated and the DoI or link to the publication for our records.
This is a searchable list of all the studies that have met out inclusion and exclusion criteria up until `r paste(max(search_details$date_screened))`. These are live links and should direct to the relevant article, however, some may have been deleted or require institutional access.
```{r tail_study_details, include=FALSE}
datatable(data_study_general[1:4] %>%
            mutate(`date_published_format(2020-05-12)` = as.Date(data_study_general$`date_published_format(2020-05-12)`),
                   doi = paste0("<a href='",doi,"' target='_blank'>",doi,"</a>")),
          colnames = c("Lead author" = 2, "Date published" = 3, "Source" = 4, "DOI" = 5),
          escape = F)
```
The third sheet produces **Table 1** this contains the details of the population of the studies in our review. Primarily includes smoking status but also the proportion of females in the study and the age of participants.
```{r tail_table_1, include=FALSE}
datatable(table_1 %>%
                 filter(lead_author != is.na(lead_author)))
```
The fourth sheet produces **Table 2** this contains the data extracted from relevant studies on testing data and smoking status. Most studies will not have data on this outcome however we filter these subsequently. These are sparse datasets as many studies do not report on all levels of smoking exposure.
```{r tail_table_2, include=FALSE}
datatable(
  table_2 %>%
  filter(data_on_testing == TRUE)
)
```
The fifth sheet produces **Table 3** this contains the data extracted from relevant studies on hospitalisation and smoking status. 
```{r tail_table_3, include=FALSE}
datatable(
  table_3 %>%
  filter(data_on_hospitalisation == TRUE)
)
```
The sixth sheet produces **Table 4** this contains the data extracted from relevant studies disease severity data and smoking status. Disease severity is differentially reported across the studies in some there is reference to WHO severity score in others we have based the distinction on clinical characteristics or whether patients were admitted to Intensive or Critical care areas.
```{r tail_table_4, include=FALSE}
datatable(
  table_4 %>%
  filter(data_disease_severity == TRUE)
)
```
The seventh sheet produces **Table 5** this contains the data extracted from relevant studies on COVID-19 related mortality and smoking status. A caution needed when interpreting this data is that most studies have not followed patients up for sufficient amounts of time to be able to accurately report on disease associated mortality.
```{r tail_table_5, include=FALSE}
datatable(
  table_5 %>%
  filter(data_on_deaths == TRUE)
)
```
The final sheet is used to collate data on **Study quality** we changed our method on assessing study quality in version 3 of the review. We use the following criteria:

@@

## Clean data and save updated versions as RDS files
The data from the google sheets document is then cleaned using a script from the `linelist` package which has been developed by T. Jombart and Z. Kamvar within the [R Epidemics Consortium](https://www.repidemicsconsortium.org/)
The script `clean_data()` ensures consistency among column names, country names, dates and missing values in the included sheets. Data is also saved as `.rds` files in the `/data_clean` folder of the project repository. 
```{r clean_data}

search_details <- search_details %>%
  clean_data() %>%
  rename(date_screened = date_screening_in_format_2020_05_22) %>%
  write_rds(here::here('data_clean', 'search_details.rds')) ## The title of the date screened column is to communicate among the review team how we need date formatted

protect_columns_1 <- names(data_study_general) %in% 'doi' ## As the DoI's are links we want to preserve their formatting when running the cleaning script

data_study_general <- data_study_general %>%
  rename(date_published = `date_published_format(2020-05-12)`) %>%
  clean_data(protect = protect_columns_1) %>%
  mutate(study_id = 1:length(lead_author)) %>% ## We create a unique study ID to aid checking of the outputs later
  write_rds(here::here('data_clean', 'data_study_general.rds'))

prisma_previous <- data_study_general

review_details <- data_study_general %>%
  select(lead_author, date_published, country, review_version, study_id) %>% ## The version of the review in which included studies were incorporated is noted
  write_rds(here::here('data_clean', 'review_details.rds'))

table_1 <- table_1 %>%
  clean_data() %>%
  mutate(., lower_range = sub('\\_.*', '', .$range)) %>%
  mutate(., upper_range = sub('.*_', '',.$range,)) %>% ## We break apart the age range into an upper and lower level
  select(lead_author, sample_size, female_sex_percent, data_source, median_age, mean_age, iqr_lower, iqr_upper, standard_deviation, lower_range,
         upper_range, current_smoker, former_smoker, current_former_smoker, never_smoker, never_smoker_unknown, current_vaper, former_vaper,
         current_former_vaper, not_stated, missing, total) %>%
  mutate(study_id = 1:length(lead_author)) %>%
  filter(!is.na(lead_author)) %>%
  left_join(., review_details %>%
              select(-"lead_author"), by = 'study_id') %>%
  write_rds(here::here('data_clean', 'table_1.rds'))

##For the following tables we're only interested in obtaining data for trials which report on the specific outcome of interest

table_2 <-  table_2 %>%
  clean_data() %>%
  mutate(study_id = 1:length(lead_author)) %>%
  filter(data_on_testing == TRUE) %>%
  left_join(., review_details %>%
              select(-"lead_author"), by = 'study_id') %>%
  write_rds(here::here('data_clean', 'table_2.rds'))

table_3 <-  table_3 %>%
  clean_data() %>%
  mutate(study_id = 1:length(lead_author)) %>%
  filter(data_on_hospitalisation == TRUE) %>%
  left_join(., review_details %>%
              select(-"lead_author"), by = 'study_id') %>%
  write_rds(here::here('data_clean', 'table_3.rds'))

table_4 <-  table_4 %>%
  clean_data() %>%
  mutate(study_id = 1:length(lead_author)) %>%
  filter(data_disease_severity == TRUE) %>%
  left_join(., review_details %>%
              select(-"lead_author"), by = 'study_id') %>%
  write_rds(here::here('data_clean', 'table_4.rds'))

table_5 <- table_5 %>%
  clean_data() %>%
  mutate(study_id = 1:length(lead_author)) %>%
  filter(data_on_deaths == TRUE) %>%
  left_join(., review_details %>%
              select(-"lead_author"), by = 'study_id') %>%
  write_rds(here::here('data_clean', 'table_5.rds'))

protect_columns_2 <- !names(table_6) %in% 'lead_author'

table_6 <-  table_6 %>%
  clean_data(protect = protect_columns_2) %>%
  mutate(study_id = 1:length(lead_author)) %>%
  left_join(., table_1 %>%
              select(not_stated,
                     missing,
                     total,
                     study_id),
                          by = 'study_id') %>%
  mutate(missingness = rowSums(.[8:9], na.rm = T),
         missingness_percentage = (missingness/total)*100) %>% ## Later we want to assess the amount of missingness for each study as it would impact the inclusion of a study into the relevant meta-analyses
  select(-c(not_stated, missing, total, missingness)) %>%
  left_join(., review_details %>%
              select(-lead_author), by = 'study_id') %>%
  write_rds(here::here('data_clean', 'table_6.rds'))

a <- data_study_general %>%
  select(lead_author, date_published, source, study_id) %>%
  rename('Lead Author' = lead_author,
         'Date Published' = date_published,
         'Publication Source' = source,
         'Study ID' = study_id)

a$`Lead Author` <- to_upper_camel_case(a$`Lead Author`, sep_out = ", ")
a$`Publication Source` <- to_title_case(a$`Publication Source`)
a$`Publication Source` <- if_else(str_length(a$`Publication Source`) < 5,
                                  toupper(a$`Publication Source`),
                                  to_title_case(a$`Publication Source`))

write_rds(data_study_general, here("data_clean", "data_study_general.rds"))
```
The package `flextable` can save tables in a format that is easily manageable within word which we currently use to write the manuscript (until I get better with RMarkdown). At various points I save these to the `output_data` folder.
``` {r save_as_table_for_word, include=FALSE}
datatable(a)

@@

# Preparing the descriptive analysis {.tabset .tabset-fade .tabset-pills}

@@

Generally we label these as _old in the Google sheet but there are exceptions to this so we manually define them at the moment.

@@

This is a searchable table.
``` {r descriptives}
data_study_general <- data_study_general %>%
  filter(review_version %in% analysed_versions) %>%
  filter(!(lead_author %in% exclude_from_analysis)) %>%
  write_rds(., here::here('data_clean', 'data_study_general.rds'))

review_details <- data_study_general %>%
  select(lead_author, date_published, country, review_version, study_id) %>% 
  filter(!(lead_author %in% exclude_from_analysis))

table_1 <- table_1 %>%
  filter(review_version %in% analysed_versions) %>%
  select(-review_version) %>%
  filter(!(lead_author %in% exclude_from_analysis))

table_2 <- table_2 %>%
  filter(review_version %in% analysed_versions) %>%
  select(-review_version) %>%
  filter(!(lead_author %in% exclude_from_analysis))

table_3 <- table_3 %>%
  filter(review_version %in% analysed_versions) %>%
  select(-review_version) %>%
  filter(!(lead_author %in% exclude_from_analysis))

table_4 <- table_4 %>%
  filter(review_version %in% analysed_versions) %>%
  select(-review_version) %>%
  filter(!(lead_author %in% exclude_from_analysis))

table_5 <- table_5 %>%
  filter(review_version %in% analysed_versions) %>%
  select(-review_version) %>%
  filter(!(lead_author %in% exclude_from_analysis))

table_6 <- table_6 %>%
  filter(review_version %in% analysed_versions) %>%
  select(-review_version) %>%
  filter(!lead_author %in% exclude_from_analysis)

a <- data_study_general %>%
  select(lead_author, date_published, source, study_id) %>%
  rename('Lead Author' = lead_author,
         'Date Published' = date_published,
         'Publication Source' = source,
         'Study ID' = study_id)

a$`Lead Author` <- to_upper_camel_case(a$`Lead Author`, sep_out = ", ")
a$`Publication Source` <- to_title_case(a$`Publication Source`)
a$`Publication Source` <- if_else(str_length(a$`Publication Source`) < 5,
                                  toupper(a$`Publication Source`),
                                  to_title_case(a$`Publication Source`))

datatable(a)

@@

# Study descriptive analysis {.tabset .tabset-fade .tabset-pills}

@@

@@

save_as_docx(a, path = here('output_data', 'Countries_performing_studies.docx'))  
```
## A map is produced for where the studies are performed
``` {r interactive global map, cache = TRUE}
library(rgdal)
library(leaflet)
library(coronavirus)
update_dataset()

@@

from_countries <- c("USA", "UK", "Iran", "South Korea")
to_countries <- c("United States", "United Kingdom", "Iran (Islamic Republic of)", "Korea, Republic of")
country_map <- country %>%
  mutate(Country = plyr::mapvalues(Country, from = from_countries,
                to = to_countries))

from_countries <- c("US", "Iran", "Korea, South", "Czech Republic")
to_countries <- c("United States", "Iran (Islamic Republic of)", "Korea, Republic of", "Czechia")

data("coronavirus")
summary_df <- coronavirus %>% 
  filter(type == "confirmed") %>%
  group_by(country) %>%
  summarise(total_cases = sum(cases)) %>%
  arrange(-total_cases) %>%
  rename("NAME" = country) %>%
  mutate(NAME = plyr::mapvalues(NAME, from = from_countries,
                to = to_countries))

@@

* **Summary statistics:** this table will give us the mean, median and IQR of the samples in the review 
``` {r numbers}
#Numbers
summary(as.numeric(table_1$sample_size))
```
* **Total number of participants**: `r paste(sum(as.numeric(table_1$sample_size)))`

## We want to know if they use a CRF or electronic health record
The majority of data on smoking outcomes is extracted from electronic health records that are routinely collected in the provision of healthcare. Some of the studies utilise specifically designed Case Report Forms (CRFs). The source of information on smoking status is not always reported.
``` {r data_source}
#Source of data
table_1$data_source %>%
  recode('electronic_health_records' = 'Electronic health record',
         'case_report_form' = 'Case report form',
         'not_stated' = 'Not stated') %>%
  table() %>%
  as.data.frame() %>%
  arrange(desc(Freq)) %>%
  rename('Data source' = 1,
         'Number' = 2) %>%
  flextable() %>%
  set_table_properties(width = 0.5, layout = 'autofit')
```

## Classification of COVID
``` {r diagnosis_method}
table(data_study_general$diagnostic_approach)
```

@@

@@

numeric_columns <- c('Median (IQR)', 'Female %', 'Current smoker %','Former smokers %', 'Current/former smokers %',
                     'Never smokers %', 'Never/unknown smokers %', 'Missing %')
```
The total number of included studies is `r paste(nrow(table_1_word))`. This table is searchable
```{r}
datatable(a) %>%
  formatRound(
    columns = c(8:14),
    digits = 2,
    interval = 3,
    mark = ",",
    dec.mark = getOption("OutDec")
)

@@

save_as_docx(a, path = here('output_data', 'Table_1.docx'))
```

@@

save_as_docx(a, path = here('output_data', 'Table_2.docx'))
```

@@

@@

save_as_docx(a, path = here('output_data', 'Table_3.docx'))
```

@@

@@

save_as_docx(a, path = here('output_data', 'Table_4.docx'))
```

### Smoking and severity meta-analysis {.tabset .tabset-fade .tabset-pills}
```{r current_never severity, echo = F}
table_4 <- table_4_word
included_studies <- quality_table_4 %>%
  filter(overall_quality != 'poor') %>%
  select(lead_author)
```
The studies included in meta-analysis are `r knitr::combine_words(pull(included_studies, lead_author))`.

@@

@@

save_as_docx(a, path = here('output_data', 'Table_5.docx'))
```

### Smoking and COVID-19 mortality meta-analysis {.tabset .tabset-fade .tabset-pills}
```{r current_never mortality, echo = F}
exclude <- c("rajter", "garassino", "holman")
table_5 <- table_5_word
included_studies <- quality_table_5 %>%
  filter(overall_quality != 'poor') %>%
  filter(!lead_author %in% exclude) %>%
  select(lead_author)
```
The studies included in meta-analysis are `r knitr::combine_words(pull(included_studies, lead_author))`.

>>>>

  html_document:
    code_folding: hide
    highlight: zenburn
    number_sections: true
    theme: spacelab
    css: !expr here::here('css', 'style.css')
    keep_md: false
editor_options: 
  chunk_output_type: inline
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = F,
                      message = F)
options(width = 180)
unlink('reports/markdown_report_cache', recursive = TRUE)
```
# Data preparation

## Load packages
* **Load packages**: All necessary packages are loaded in from the `libraries.r` script in the `/scripts` folder.
* **Author dictionary**: An author dictionary is created to manage the presentation of author names in the final tables and meta-analyses
* **Load scripts**: We have written functions to handle much of the Bayesian analysis
* **Load Bayesian datasets**: The Bayesian approach relies on large simulated datasets from the observed data, for this report we only present the results graphically from data simulated outside of the report. The scripts `bayes_scripts.R`, `bayesian_data_generation.R` and `bayesian_analysis.R` should be able to be run locally to generate your own simulated data.

The code is all stored in the GitHub repository [here](https://github.com/DidDrog11/smoking_covid/tree/master)
```{r load_packages, include=FALSE, quietly=T}
source(here::here("scripts", "libraries.R"))
```

```{r load_dictionary}
source(here("scripts", "author_dictionary.R"))
```
## Download data
This is relatively automated in this script however, if you don't have an API key you can download the file individually and store it in the `/data_spreadsheet` folder as `data_extraction_current.xlsx`, the sheets are then extracted from the file.
``` {r google_data}
google_api <- rstudioapi::askForSecret("Google API Key")
register_google(google_api)
drive_download("https://docs.google.com/spreadsheets/d/1jelIGxrm99QpDKwSoyMUliDJQWtzk4bHsNGDaIjxTaU/edit?usp=sharing", path = here("data_spreadsheet", "data_extraction_current.xlsx"), overwrite = T)

@@

@@

```{r head_search_details}
flextable(search_details[,1:13])
```
The second sheet is **General study details** this includes the lead author, where the study is published, the date it was published, the country in which the data originated and the DoI or link to the publication for our records.

This is a searchable list of all the studies that have met out inclusion and exclusion criteria up until `r paste(max(search_details$date_screened))`. These are live links and should direct to the relevant article, however, some may have been deleted or require institutional access.
```{r tail_study_details, include=FALSE}
datatable(data_study_general[1:4] %>%
            mutate(`date_published_format(2020-05-12)` = as.Date(data_study_general$`date_published_format(2020-05-12)`),
                   doi = paste0("<a href='",doi,"' target='_blank'>",doi,"</a>")),
          colnames = c("Lead author" = 2, "Date published" = 3, "Source" = 4, "DOI" = 5),
          escape = F)
```
The third sheet produces **Table 1** this contains the details of the population of the studies in our review. Primarily includes smoking status but also the proportion of females in the study and the age of participants.
```{r tail_table_1, include=FALSE}
datatable(table_1 %>%
                 filter(lead_author != is.na(lead_author)))
```
The fourth sheet produces **Table 2** this contains the data extracted from relevant studies on testing data and smoking status. Most studies will not have data on this outcome however we filter these subsequently. These are sparse datasets as many studies do not report on all levels of smoking exposure.
```{r tail_table_2, include=FALSE}
datatable(
  table_2 %>%
  filter(data_on_testing == TRUE)
)
```
The fifth sheet produces **Table 3** this contains the data extracted from relevant studies on hospitalisation and smoking status. 
```{r tail_table_3, include=FALSE}
datatable(
  table_3 %>%
  filter(data_on_hospitalisation == TRUE)
)
```
The sixth sheet produces **Table 4** this contains the data extracted from relevant studies disease severity data and smoking status. Disease severity is differentially reported across the studies in some there is reference to WHO severity score in others we have based the distinction on clinical characteristics or whether patients were admitted to Intensive or Critical care areas.
```{r tail_table_4, include=FALSE}
datatable(
  table_4 %>%
  filter(data_disease_severity == TRUE)
)
```
The seventh sheet produces **Table 5** this contains the data extracted from relevant studies on COVID-19 related mortality and smoking status. A caution needed when interpreting this data is that most studies have not followed patients up for sufficient amounts of time to be able to accurately report on disease associated mortality.
```{r tail_table_5, include=FALSE}
datatable(
  table_5 %>%
  filter(data_on_deaths == TRUE)
)
```
The final sheet is used to collate data on **Study quality**. The method of assessing quality changed in version 3 of the review. We now use the following criteria:

@@

## Clean data and save updated versions as RDS files
The data from the google sheets document is then cleaned using a script from the `linelist` package which has been developed by T. Jombart and Z. Kamvar within the [R Epidemics Consortium](https://www.repidemicsconsortium.org/)
The function `clean_data()` ensures consistency among column names, country names, dates and missing values in the included sheets. Data is also saved as `.rds` files in the `/data_clean` folder of the project repository. 
```{r clean_data}
source(here("scripts", "clean_data.r"))
```
The package `flextable` can save tables in a format that is easily manageable within word which we currently use to write the manuscript (until I get better with RMarkdown). At various points I save these to the `output_data` folder.
``` {r save_as_table_for_word, include=FALSE}
datatable(a)

@@

# Preparing the descriptive analysis

@@

Generally we label these as _old in the Google sheet but there are exceptions to this so we manually define them.

@@

This is a searchable table.
``` {r descriptives}
source(here("scripts", "remove_excluded.r"))
datatable(a)

@@

# Study descriptive analysis

@@

all_countries <- country %>%
  group_split(-Number)

@@

save_as_docx(a, path = here('output_data', 'Countries_performing_studies.docx'))  
```
## A map is produced for where the studies are performed
``` {r interactive global map, cache = TRUE}
library(rgdal)
library(leaflet)
library(coronavirus)

@@

from_countries <- c("USA", "UK", "Iran",  "Korea, South")
to_countries <- c("United States", "United Kingdom", "Iran (Islamic Republic of)", "Korea, Republic of")
country_map <- country %>%
  mutate(Country = plyr::mapvalues(Country, from = from_countries,
                to = to_countries))

refresh_coronavirus_jhu()
data("coronavirus")
summary_df <- coronavirus %>% 
  filter(type == "confirmed") %>%
  group_by(country) %>%
  summarise(total_cases = sum(cases)) %>%
  arrange(-total_cases) %>%
  rename("NAME" = country) %>%
  mutate(NAME = plyr::mapvalues(NAME, from = from_countries,
                to = to_countries))

@@

* **Summary statistics:** this table will give us the mean, median and IQR of the samples in the review 
``` {r numbers}
#Numbers
participants <- summary(as.numeric(table_1$sample_size))
```
* **Total number of participants**: `r paste(sum(as.numeric(table_1$sample_size)))`

## We want to know if they use a CRF or electronic health record
The majority of data on smoking outcomes is extracted from electronic health records that are routinely collected in the provision of healthcare. Some of the studies utilise specifically designed Case Report Forms (CRFs). The source of information on smoking status is not always reported.
``` {r data_source}
#Source of data
data_source <- table_1$data_source %>%
  recode('electronic_health_records' = 'Electronic health record',
         'case_report_form' = 'Case report form',
         'not_stated' = 'Not stated') %>%
  table() %>%
  as.data.frame() %>%
  arrange(desc(Freq)) %>%
  rename('Data source' = 1,
         'Number' = 2)

data_source %>%
  flextable() %>%
  set_table_properties(width = 0.5, layout = 'autofit')
```

## Classification of COVID
``` {r diagnosis_method}
diagnostics <- table(data_study_general$diagnostic_approach)
diagnostics
```

@@

fair_quality_number <- quality_rating %>%
  filter(overall_quality == "fair")

poor_quality_number <- quality_rating %>%
  filter(overall_quality == "poor")

@@

numeric_columns <- c('Median (IQR)', 'Female %', 'Current smoker %','Former smokers %', 'Current/former smokers %',
                     'Never smokers %', 'Never/unknown smokers %', 'Missing %')

saveRDS(a, file = here("data_clean", "table_1_refs.rds"))
source(here("scripts", "references_in_table.r"))
```
The total number of included studies is `r paste(nrow(table_1_word))`. This table is searchable
```{r}
datatable(a) %>%
  formatRound(
    columns = c(8:14),
    digits = 2,
    interval = 3,
    mark = ",",
    dec.mark = getOption("OutDec")
)

@@

saveRDS(a, file = here("reports", "tables", "table_1.rds"))
save_as_docx(a, path = here('output_data', 'Table_1.docx'))
```

@@

saveRDS(a, file = here("reports", "tables", "table_2.rds"))
save_as_docx(a, path = here('output_data', 'Table_2.docx'))
```

@@

good_quality_2 <- quality_table_2 %>%
  filter(overall_quality != 'good')

fair_quality_2 <- quality_table_2 %>%
  filter(overall_quality != 'fair')

@@

saveRDS(a, file = here("reports", "tables", "table_3.rds"))
save_as_docx(a, path = here('output_data', 'Table_3.docx'))
```

@@

fair_quality_3 <- quality_table_3 %>%
  filter(overall_quality != 'fair')

@@

saveRDS(a, file = here("reports", "tables", "table_4.rds"))
save_as_docx(a, path = here('output_data', 'Table_4.docx'))
```

### Smoking and severity meta-analysis {.tabset .tabset-fade .tabset-pills}
```{r current_never severity, echo = F}
table_4 <- table_4_word
included_studies <- quality_table_4 %>%
  filter(overall_quality != 'poor') %>%
  select(lead_author)

fair_quality_4 <- quality_table_4 %>%
  filter(overall_quality == 'fair')
```
The studies included in meta-analysis are `r knitr::combine_words(pull(included_studies, lead_author))`.

@@

fair_quality_5 <- quality_table_5 %>%
  filter(overall_quality != 'fair')

@@

saveRDS(a, file = here("reports", "tables", "table_5.rds"))
save_as_docx(a, path = here('output_data', 'Table_5.docx'))
```

### Smoking and COVID-19 mortality meta-analysis {.tabset .tabset-fade .tabset-pills}
```{r current_never mortality, echo = F}
exclude <- c("rajter", "garassino", "holman")
table_5 <- table_5_word
included_studies <- quality_table_5 %>%
  filter(overall_quality != 'poor') %>%
  filter(!lead_author %in% exclude) %>%
  select(lead_author)

fair_quality_4 <- quality_table_5 %>%
  filter(overall_quality != 'fair')
```
The studies included in meta-analysis are `r knitr::combine_words(pull(included_studies, lead_author))`.
